Board games group recomendation using metadata

### 2024-12-09 paper v2/paper v2.tex
Resultados paper

\subsection{Recommendation}
The third stage consists of recommending games to groups of players based on their preferences. Since the recommendations are supposed to be made to groups, the preferences of the group are calculated using a variety of methods, that can be described as follows:
\begin{enumerate}
    \item Simple average: The preferences of the group are calculated as the simple average of the preferences of the individual players.
    \item Least misery: The preferences of the group are calculated as the minimum of the preferences of the individual players.
    \item ... % asegurarse que esto está al día con lo que presentemos al final del trabajo
\end{enumerate}

@@

>>>>

\subsection{Recommendation}
The third stage consists of recommending games to groups of players based on their preferences. Since the recommendations are supposed to be made to groups, the preferences of the group are calculated using a variety of methods, that can be described as follows:
\begin{enumerate}
    \item Simple average: The preferences of the group are calculated as the simple average of the preferences of the individual players based on a top-100 recommendation list prior to the group formation. This can be done with the following formula:
    \begin{equation}
        \text{avg\_score\_item} = \frac{\sum_{i=1}^{n} \text{user\_rating}_i}{n}
    \end{equation}
    with $n$ being the number of users in the group, and $u_i$ being the rating of the $i$-th user given an item.
    % \item Least misery: The preferences of the group are calculated as the minimum of the preferences of the individual players.
    % \item ... % asegurarse que esto está al día con lo que presentemos al final del trabajo
\end{enumerate}

Given the method explained above, we assign the score to each of the items in the top-100 recommedation list of each user on a group. Then we create a new list of items combining the top-100 recommendation lists of each user on a group, and we extract the top-n items with the highest average scores. Note that for this to work properly, if two users have a matching item in their top-100 recommendation list, the item will only be included as the sum of the average rankings by the users in the group.

@@

For each metric, we used a cumulative avarage of the results of 300 different group formations, on which we applied the common formulas for each metric. Meaning that for each group, we calculated all of the metrics mentioned above, then we added them and divided by the number of groups.
\newline
